---
format:
  pdf:
    documentclass: article
    geometry:
      - margin=1in
    keep-tex: false
editor: source
header-includes:
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{xcolor}
  - \usepackage{titlesec}
  - \usepackage{booktabs}
  - \definecolor{lightgray}{gray}{0.5}
  - \titleformat{\section}{\Large\bfseries}{}{0em}{}[\titlerule]
---

\pagenumbering{gobble}

```{=latex}
\noindent
\begin{minipage}[t]{0.65\textwidth}
  \Huge \textbf{Michael Asger Andersen}
\end{minipage}%
\begin{minipage}[t]{0.35\textwidth}
  \raggedleft
  \small
  \textbf{Mobile:} +45 31770856 \\
  \textbf{Email:} michaelasger@gmail.com \\
  \textbf{ORCID:} 0000-0001-9729-9974 \\
  \textbf{Website:} https://masger.github.io
\end{minipage}
```

\vspace{0.5cm}
\hrule
\vspace{0.5cm}

\section*{Research interests}
My research examines how pharmacogenetic testing can be translated into better clinical outcomes by linking insights from large-scale registry data with prospective clinical interventions. I focus on cardiovascular pharmacogenetics, including implementation of CYP2C19-guided antiplatelet therapy and investigation of SLCO1B1-mediated statin intolerance.

```{r, message=FALSE, warning=FALSE, echo=FALSE, results='asis'}
library(tidyverse)
library(knitr)
library(glue)
library(data.table)
library(readxl)

# Read data
cv_entries <- read_csv("cv_data_maa_updated.csv", col_types = cols(.default = "c")) |> setDT()

# Process dates
# Fix: Handle ISO date strings from CSV instead of Excel numeric dates
cv_entries[, real_date := as.Date(date)]
cv_entries[, real_date_end := suppressWarnings(as.Date(date_end))]

cv_entries[
  , year_end := fifelse(date_end == "present", "present", as.character(year(real_date_end)))]

cv_entries[,
         year := fifelse(!is.na(year_end), paste0(year(real_date), "--", year_end), as.character(year(real_date)))]

cv_entries = cv_entries[order(type,-real_date)]

# Helper to print table rows
print_section <- function(data) {
  cat("\\begin{longtable}{@{}p{0.15\\textwidth} p{0.82\\textwidth}@{}}\n")

  for(i in 1:nrow(data)) {
    # Escape special characters
    what_text <- str_replace_all(data$what[i], "~", "$\\\\approx$")
    what_text <- str_replace_all(what_text, "&", "\\\\&")
    what_text <- str_replace_all(what_text, "%", "\\\\%")

    # Year in gray
    cat(glue("\\textcolor{{lightgray}}{{{data$year[i]}}} & {what_text} \\\\"), "\n")
    cat("\\addlinespace[0.2cm]\n")
  }

  cat("\\end{longtable}\n")
}
```

\section*{Education}

```{r, message=FALSE, warning=FALSE, echo=FALSE, results='asis'}
edu <- cv_entries |>
  filter(type == 'education') |>
  mutate(what = fifelse(what == "PhD",glue("\\textbf{{{what}}}, {where} \\newline ",
                      "{additional_info} \\newline ",
                      "\\textit{{{additional_info2}}}"),
                      glue("\\textbf{{{what}}}, {where}"))) |>
  select(year, what)

print_section(edu)
```

\section*{Professional experience}

```{r, message=FALSE, warning=FALSE, echo=FALSE, results='asis'}
pos <- cv_entries |>
  filter(type == 'positions', is.na(exclude)) |>
  mutate(what = case_when(
    !is.na(additional_info) & !is.na(where) ~ glue("\\textbf{{{what}}} {where} \\newline {additional_info}"),
    !is.na(additional_info) & is.na(where) ~ glue("\\textbf{{{what}}} \\newline {additional_info}"),
    is.na(additional_info) & !is.na(where) ~ glue("\\textbf{{{what}}} {where}"),
    TRUE ~ glue("\\textbf{{{what}}}")
  )) |>
  select(year, what)

print_section(pos)
```

\section*{Major grants and funding (Principal Investigator: $\approx$DKK 5.6 million)}

```{r, message=FALSE, warning=FALSE, echo=FALSE, results='asis'}
grants <- cv_entries |>
  filter(type == 'major_grants') |>
  mutate(what = if_else(is.na(additional_info),
                        glue("\\textbf{{{what}}} ({additional_info2}), {where}"),
                        glue("\\textbf{{{what}}} ({additional_info2}), {where}. \\newline {additional_info}"))) |>
  select(year, what)

print_section(grants)
```

\section*{Awards \& honours}

```{r, message=FALSE, warning=FALSE, echo=FALSE, results='asis'}
awards <- cv_entries |>
  filter(type == 'awards') |>
  mutate(what = if_else(!is.na(where),
                        glue("\\textbf{{{what}}}, {where}"),
                        glue("\\textbf{{{what}}}"))) |>
  select(year, what)

print_section(awards)
```

\section*{Teaching experience}

```{r, message=FALSE, warning=FALSE, echo=FALSE, results='asis'}
teaching <- cv_entries |>
  filter(type == 'teaching') |>
  mutate(what = case_when(
    !is.na(institution) & !is.na(where) ~ glue("\\textbf{{{what}}}, {institution}, {where} \\newline {additional_info}"),
    !is.na(institution) & is.na(where) ~ glue("\\textbf{{{what}}}, {institution} \\newline {additional_info}"),
    is.na(institution) & !is.na(where) ~ glue("\\textbf{{{what}}}, {where} \\newline {additional_info}"),
    TRUE ~ glue("\\textbf{{{what}}} \\newline {additional_info}")
  )) |>
  select(year, what)

print_section(teaching)
```

\section*{Supervision}

\begin{itemize}
    \item \textbf{Primary Supervisor for PhD student}: Present (1); Graduated (0), if the current grant is awarded I will be primary supervisor for two PhD students.
    \item \textbf{Co-Supervisor for PhD students}: Present (0); Graduated (1):
    \item \textbf{Primary Supervisor for master and bachelor students}: Present (1); Graduated (4)
\end{itemize}

\section*{Academic Commissions}

```{r, message=FALSE, warning=FALSE, echo=FALSE, results='asis'}
comm <- cv_entries |>
  filter(type == 'academic_commisions') |>
  mutate(what = glue("\\textbf{{{what}}}, {where}")) |>
  select(year, what)

print_section(comm)
```

\section*{Clinical Guidelines}

\begin{itemize}
    \item \textbf{CPIC NAT2 guideline}: Participant in the working group
    \item \textbf{Medical Genetics Summaries}: Simvastatin Therapy and SLCO1B1 Genotype : Reviewer
\end{itemize}

\section*{Publications}

\begin{itemize}
    \item \textbf{Total Peer-review publications}: 41
    \item \textbf{First and last author publications}: 7 (1 as shared last author)
    \item \textbf{H-index}: 17 (Google scholar, December 2025)
    \item \textbf{Citations}: 887 (Google scholar, December 2025)
\end{itemize}
