---
output:
  pagedown::html_paged:
    number_sections: false
    css: ["css/academic_cv.css"]
links-to-footnotes: false
knit: pagedown::chrome_print
editor_options:
  chunk_output_type: console
spacing: single
---

<style>
:root{
  --last-updated: "\00a0 \00a0 \00a0 \00a0 Last updated: `r format(Sys.Date(), '%B, %Y')`";
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(knitr)
library(glue)
library(fontawesome)
library(readxl)
library(lubridate)
library(data.table)
source("R/utility-functions.R")

cv_entries <- read_csv("cv_data_maa_updated.csv") |> setDT()
cv_entries[
  , c("real_date", "real_date_end") := .(
    as.Date(date),
    as.Date(as.numeric(date_end), origin = "1900-01-01")
  )
]
cv_entries[
  , year_end := fifelse(date_end == "present", "present", as.character(year(real_date_end)))
]

cv_entries[
  ,
  year := fifelse(!is.na(year_end), paste0(year(real_date), "---", year_end), as.character(year(real_date)))
]

cv_entries <- cv_entries[order(type, -real_date)]

publications <- read_excel("cv_data.xlsx", sheet = "publications") |>
  mutate(year = year(date))
```

::: {.title-and-contact}

:::::: {.title}
<h1 class="title">Michael Asger Andersen</h1>
::::::

:::::: {.contact-info}
**Born:** November 13, 1987 in Roskilde<br>
**Mobile:** +45 31770856<br>
**Email:** michaelasger@gmail.com<br>
**ORCID:** 0000-0001-9729-9974<br>
**Website:** https://masger.github.io<br>
::::::

:::

::: {.cv-entries}

### Research interests
My research examines how pharmacogenetic testing can be translated into better clinical outcomes by linking insights from large-scale registry data with prospective clinical interventions. I focus on cardiovascular pharmacogenetics, including implementation of CYP2C19-guided antiplatelet therapy and investigation of SLCO1B1-mediated statin intolerance.

### Education
```{r}
cv_entries |>
  filter(type == "education") |>
  mutate(what = fifelse(
    what == "PhD", glue(
      "<span class='cv-entry-title'>{what}</span>, {where}<br>",
      "{additional_info}<br>",
      "<span class='thesis-title'>{additional_info2}</span>"
    ),
    glue("<span class='cv-entry-title'>{what}</span>, {where}")
  )) |>
  select(year, what) |>
  kable()
```

### Professional experience
```{r}
cv_entries |>
  filter(type == "positions", is.na(exclude)) |>
  mutate(what = case_when(
    !is.na(additional_info) & !is.na(where) ~ glue("<span class='cv-entry-title'>{what}</span>", " {where}<br>{additional_info}"),
    !is.na(additional_info) & is.na(where) ~ glue("<span class='cv-entry-title'>{what}</span><br>{additional_info}"),
    is.na(additional_info) & !is.na(where) ~ glue("<span class='cv-entry-title'>{what}</span>", " {where}"),
    TRUE ~ glue("<span class='cv-entry-title'>{what}</span>")
  )) |>
  select(year, what) |>
  kable()
```


### Major grants and funding
```{r}
cv_entries |>
  filter(type == "major_grants") |>
  mutate(what = if_else(is.na(additional_info),
    glue("<span class='cv-entry-title'>{what}</span> ({additional_info2}), {where}"),
    glue("<span class='cv-entry-title'>{what}</span> ({additional_info2}), {where}.<br>{additional_info}")
  )) |>
  select(year, what) |>
  manual_page_break_after_row("what", "Maureen Freed") |>
  kable()
```

### Awards & honours
```{r}
cv_entries |>
  filter(type == "awards") |>
  mutate(what = if_else(!is.na(where),
    glue("<span class='cv-entry-title'>{what}</span>, {where}"),
    glue("<span class='cv-entry-title'>{what}</span>")
  )) |>
  blank_year_when_repeated() |>
  select(year, what) |>
  kable()
```

### Teaching experience
```{r}
cv_entries |>
  filter(type == "teaching") |>
  mutate(what = glue(
    "<span class='cv-entry-title'>{what}</span>,{institution}, {where}<br>",
    "{additional_info}"
  )) |>
  select(year, what) |>
  manual_page_break_after_row("what", "Lecturer") |>
  kable()
```

### Supervision
- Primary Supervisor for PhD student: Present (1); Graduated (0), if the current grant is awarded I will be primary supervisor for two PhD students.
- Co-Supervisor for PhD students: Present (0); Graduated (1):
- Primary Supervisor for master and bachelor students: Present (1); Graduated (4)

### Academic Commissions
```{r}
cv_entries |>
  filter(type == "academic_commisions") |>
  mutate(what = glue("<span class='cv-entry-title'>{what}</span>, {where}")) |>
  blank_year_when_repeated() |>
  select(year, what) |>
  kable()
```

### Clinical Guidelines
- CPIC NAT2 guideline: Participant in the working group
- Medical Genetics Summaries: Simvastatin Therapy and SLCO1B1 Genotype : Reviewer

### Publications
- Total Peer-review publications: 41
- First and last author publications: 7 (1 as shared last author)
- H-index: 17 (Google scholar, December 2025)
- Citations 887 (Google scholar, December 2025)

<!-- <br class="pageBreak"> -->

:::
